---
title: "Trycycler consistency tests"
date: "2020-12-18"
author: "Ryan Wick"
output:
  html_document:
    pandoc_args: ["+RTS", "-K64m", "-RTS", "--self-contained",]
    df_print: paged
    keep_md: false
    toc: true
    toc_float: true
---

This document contains the R code used to generate plots for the consistency tests part of my Trycycler paper.

This script is licensed under a Creative Commons Attribution 4.0 International License. You should have received a copy of the license along with this work. If not, see <http://creativecommons.org/licenses/by/4.0/>.


## Load libraries

```{r}
library(tidyverse)
library(knitr)
library(cowplot)
library(scales)
```


## Output settings

```{r}
opts_chunk$set(fig.width=8, fig.height=5, dpi=300, fig.path='./plots/', echo=TRUE, dev=c('png','pdf'), warning=FALSE, message=FALSE)
pdf.options(useDingbats = FALSE)
```


## Load data

Load the distances between assemblies and the polished reference:
```{r}
load_distances_to_ref <- function(filename) {
  distances <- read_delim(filename, "\t", escape_double = FALSE, col_names = FALSE, trim_ws = TRUE, skip = 1)
  distances %>% select(X1, X2) -> distances
  colnames(distances) <- c("Assembler", "Distance")
  distances$Assembler <- str_replace(distances$Assembler, "trycycler_.+", "trycycler")
  distances %>% filter(Assembler != "polished") -> distances
  distances$Assembler <- str_to_title(distances$Assembler)
  distances$Assembler <- factor(distances$Assembler, levels = c("Miniasm", "Raven", "Flye", "Trycycler"))
  return(distances)
}
distances_1 <- load_distances_to_ref("assemblies/grouped_contigs/Acinetobacter_baumannii_J9_chromosome/distances_per_mbp.phylip")
distances_2 <- load_distances_to_ref("assemblies/grouped_contigs/Citrobacter_koseri_MINF_9D_chromosome/distances_per_mbp.phylip")
distances_3 <- load_distances_to_ref("assemblies/grouped_contigs/Enterobacter_kobei_MSB1_1B_chromosome/distances_per_mbp.phylip")
distances_4 <- load_distances_to_ref("assemblies/grouped_contigs/Haemophilus_M1C132_1_chromosome/distances_per_mbp.phylip")
distances_5 <- load_distances_to_ref("assemblies/grouped_contigs/Klebsiella_oxytoca_MSB1_2C_chromosome/distances_per_mbp.phylip")
distances_6 <- load_distances_to_ref("assemblies/grouped_contigs/Klebsiella_variicola_INF345_chromosome/distances_per_mbp.phylip")

distances_to_ref <- bind_rows(distances_1, distances_2)
distances_to_ref <- bind_rows(distances_to_ref, distances_3)
distances_to_ref <- bind_rows(distances_to_ref, distances_4)
distances_to_ref <- bind_rows(distances_to_ref, distances_5)
distances_to_ref <- bind_rows(distances_to_ref, distances_6)

distances_to_ref$Distance_log <- log10(distances_to_ref$Distance)
```

Load the distances between Trycycler assemblies:
```{r}
load_trycycler_distances <- function(filename) {
  distances <- read_delim(filename, "\t", escape_double = FALSE, col_names = FALSE, trim_ws = TRUE, skip = 1)
  distances %>% remove_rownames %>% column_to_rownames(var="X1") -> distances
  colnames(distances) <- rownames(distances)
  distances %>% select(contains("trycycler_")) -> distances
  as_tibble(cbind(nms = names(distances), t(distances))) -> distances
  distances %>% select(contains("trycycler_")) -> d
  stopifnot(dim(d) == c(6, 6))
  distances = c(d[[1,2]], d[[1,3]], d[[1,4]], d[[1,5]], d[[1,6]], d[[2,3]], d[[2,4]], d[[2,5]], d[[2,6]], d[[3,4]], d[[3,5]], d[[3,6]], d[[4,5]], d[[4,6]], d[[5,6]])
  distances <- as_tibble(distances)
  colnames(distances) <- c("Distance")
  distances$Assembler <- rep("trycycler", 15)
  distances$Assembler <- str_to_title(distances$Assembler)
  distances$Distance <- as.numeric(distances$Distance)
  return(distances)
}
distances_1 <- load_trycycler_distances("assemblies/grouped_contigs/Acinetobacter_baumannii_J9_chromosome/distances_per_mbp.phylip")
distances_2 <- load_trycycler_distances("assemblies/grouped_contigs/Citrobacter_koseri_MINF_9D_chromosome/distances_per_mbp.phylip")
distances_3 <- load_trycycler_distances("assemblies/grouped_contigs/Enterobacter_kobei_MSB1_1B_chromosome/distances_per_mbp.phylip")
distances_4 <- load_trycycler_distances("assemblies/grouped_contigs/Haemophilus_M1C132_1_chromosome/distances_per_mbp.phylip")
distances_5 <- load_trycycler_distances("assemblies/grouped_contigs/Klebsiella_oxytoca_MSB1_2C_chromosome/distances_per_mbp.phylip")
distances_6 <- load_trycycler_distances("assemblies/grouped_contigs/Klebsiella_variicola_INF345_chromosome/distances_per_mbp.phylip")

trycycler_distances <- bind_rows(distances_1, distances_2)
trycycler_distances <- bind_rows(trycycler_distances, distances_3)
trycycler_distances <- bind_rows(trycycler_distances, distances_4)
trycycler_distances <- bind_rows(trycycler_distances, distances_5)
trycycler_distances <- bind_rows(trycycler_distances, distances_6)

trycycler_distances$Distance_log <- log10(trycycler_distances$Distance)
```


Plot distances:
```{r distance_plots, fig.width = 7, fig.height = 2.3, useDingbats = FALSE}
colour_scale <- scale_fill_manual("Assembler",
                    values = c("#e89133", "#e5e82a", "#1ee46b", "#91c5ff"),
                    limits = c("Miniasm", "Raven",   "Flye",    "Trycycler"))

p1 <- ggplot(distances_to_ref, aes(x = Assembler, y = Distance, fill = Assembler)) +
  geom_dotplot(stackdir = "center", binaxis = "y", binwidth = 0.093) +
  theme_bw() + theme(legend.position = "none") +
  colour_scale + 
  scale_y_log10(limits=c(30, 3200), breaks=c(30, 100, 300, 1000, 3000), minor_breaks=NULL) +
  labs(title = "Assemblies vs hybrid-polished reference", x = NULL, y = "Differences per Mbp")

p2 <- ggplot(trycycler_distances, aes(x = Assembler, y = Distance, fill = Assembler)) +
  geom_dotplot(stackdir = "center", binaxis = "y", binwidth = 0.093) +
  theme_bw() + theme(legend.position = "none") +
  colour_scale + 
  scale_y_log10(limits=c(30, 3200), breaks=c(30, 100, 300, 1000, 3000), minor_breaks=NULL) +
  labs(title = "Trycycler vs Trycycler", x = NULL, y = "Differences per Mbp")

plot_grid(p1, p2, nrow = 1, ncol = 2, align="v", rel_widths = c(11, 6))
```

```{r distance_plots, fig.width = 7, fig.height = 2.3, useDingbats = FALSE}
colour_scale <- scale_fill_manual("Assembler",
                    values = c("#e89133", "#e5e82a", "#1ee46b", "#91c5ff"),
                    limits = c("Miniasm", "Raven",   "Flye",    "Trycycler"))

p1 <- ggplot(distances_to_ref, aes(x = Assembler, y = Distance, fill = Assembler)) +
  geom_dotplot(stackdir = "center", binaxis = "y", binwidth = 100) +
  theme_bw() + theme(legend.position = "none") +
  colour_scale + 
  scale_y_continuous(limits=c(0, 3200)) +
  labs(title = "Assemblies vs hybrid-polished reference", x = NULL, y = "Differences per Mbp")

p2 <- ggplot(trycycler_distances, aes(x = Assembler, y = Distance, fill = Assembler)) +
  geom_dotplot(stackdir = "center", binaxis = "y", binwidth =  100) +
  theme_bw() + theme(legend.position = "none") +
  colour_scale + 
  scale_y_continuous(limits=c(0, 3200)) +
  labs(title = "Trycycler vs Trycycler", x = NULL, y = "Differences per Mbp")

plot_grid(p1, p2, nrow = 1, ncol = 2, align="v", rel_widths = c(11, 6))
```
